\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-01-23 manuscript/manuscript.tex
some changes

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is gamma. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\phi$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values 
for the test when applied to samples from the same data generating process.

@@

Like we did to see if the test holds its size, we generated time series with 
marginal distributions $N(8, 8)$ and 
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. However, 
to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is gamma. Because the support of $N(8, 8)$ is
$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
values less than or equal to 0.
When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is normal. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\phi$, and $n$, we replicate the method $1000$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.

>>>>

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}\mc{addressed}
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{100, 200, 400, 800, 1600, 3200\}$. These distributions
were chosen to compare results on normal and non-normal
error structures, and the parameters were chosen so that the distributions
have the same mean 8 and variance 8. To generate 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is gamma. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\phi$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values 
for the test when applied to samples from the same data generating process.

@@

Like we did to see if the test holds its size, we generated time series with 
marginal distributions $N(8, 8)$ and 
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{200, 400, 800\}$. However, 
to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is gamma. Because the support of $N(8, 8)$ is
$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
values less than or equal to 0.
When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is normal. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\phi$, and $n$, we replicate the method $1000$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.
